---
title: "Assignment 2"
author: "Choudhary"
date: "2026-09-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```
# Task 1
# We have created a relative path for collegedata.
```{r}
college.data <- read.csv("collegedata.csv")
```

# Task 2
# This dataset contains 12 columns and 7175 rows.
```{r}
ncol(college.data)
nrow(college.data)
```


# Task 3
# We now have a dataset that has 3 columns: Institution Name, Sat Average, and Admission Rate, and 7,175 rows. 
```{r}
college.1 <- college.data %>%
  dplyr::select(INSTNM, SAT_AVG, ADM_RATE)

college.1
```

#Task 4
# I removed all the na values and plotted the average SAT Score for students and the admissions rate on the y-axis. There does not appear to be a strong correlation between SAT Score and Admissions, and the majority of scores 900-1180. 
```{r}
ggplot(college.1, aes(x = SAT_AVG, y = ADM_RATE))+geom_point(na.rm = TRUE)+
  labs(title = "College Admissions")
```


